Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
Edit results section

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test3.eps}
\caption{ASSR: $p@k$ obtained for MFCCs and scattering with logarithmic compression}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test2.eps}
\caption{ASSR: $p@k$ obtained for scattering with and without logarithmic compression (w/o log)}
\label{fig:ASS_2}
\end{center}
\end{figure}

@@

This section present evaluation results for the ASSR settings. The $p@k$ for different settings are showed in the Figures~\ref{fig:ASS_1} and \ref{fig:ASS_2}.

\subsection*{MFCC \vs scattering transform}

Irrespective of the rank $k$ considered, best result is achieved for the scattering transform with logarithmic compression using the \emph{ob-c} approach. Overall, log-compressed scattering coefficients systematically outperform MFCCs.

\subsection*{Object-based \vs early integration}

For the scattering, \emph{ob-c} and \emph{ob-w} outperform \emph{early}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} perform equivalently to \emph{early}, which shows that the discriminant information is not carried by all the centroids. To take advantage of an object-based representation, a selection step has to be run on the representatives of the scenes. Furthermore It appears that \emph{ob-c} is be able to better characterize the classes than \emph{ob-w}. This last observation suggests that weighted a centroid according to the number of frames belonging to it may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources.

For the MFCCs, there is no clear evidence that the \emph{ob} approaches improve the results.

\subsection*{Role of logarithmic compression}

Outcomes for the scattering with and without logarithmic compression are showed in Figure~\ref{fig:ASS_2}. It can be seen that the logarithmic compression strongly improves the results, specially for the \emph{ob} approaches, which perform lesser than \emph{early} without the logarithmic compression. \gl{une idée du pourquoi ?}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/supervised_rbf_test3.eps}
\caption{...}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test3.eps}
\caption{ASSR: $p@k$ obtained for MFCCs and scattering with logarithmic compression.}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test2.eps}
\caption{ASSR: $p@k$ obtained for scattering with and without logarithmic compression.}
\label{fig:ASS_2}
\end{center}
\end{figure}

@@

This section presents evaluation results for the ASSR settings. The $p@k$ for different settings are shown in Figures \ref{fig:ASS_1} and \ref{fig:ASS_2}, illustrating the effect of the different similarity metrics and the influence of the logarithm, respectively.

\subsubsection*{MFCC \vs scattering transform}

Irrespective of the rank $k$ considered, best result is achieved for the scattering transform with logarithmic compression using the \emph{ob-c} approach. Overall, log-compressed scattering coefficients systematically outperform MFCCs. This is to be expected since the scattering coefficients capture larger-scale modulations as opposed to the MFCCs which only describe the short-time spectral envelope.

\subsubsection*{Object-based \vs early integration}

For the scattering transform, \emph{ob-c} and \emph{ob-w} outperform \emph{early}, thus confirming the benefits of using an object-based representation to refine the similarity measures between the scenes. However, it is worth noticing that \emph{ob-a} perform equivalently to \emph{early}, which shows that the discriminant information is destroyed by averaging the contributions from all centroids. To take advantage of an object-based representation, we need to select certain representative centroids when comparing objects. Furthermore, it appears that \emph{ob-c} is be able to better characterize the classes than \emph{ob-w}. This last observation suggests that weighting a centroid according to the number of frames it contains may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may shared a lot of similar sound sources with only a few sources discriminating between them.

For the MFCCs, there is no clear evidence that the \emph{ob} approaches improve the results. \ja{Why?}

\subsubsection*{Role of logarithmic compression}

Outcomes for the scattering with and without logarithmic compression are shown in Figure \ref{fig:ASS_2}. It can be seen that the logarithmic compression strongly improves the results, especially for the \emph{ob} approaches, which perform worse than \emph{early} without the logarithmic compression. \gl{une idée du pourquoi ?}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{gfx/supervised_rbf_test3.eps}
\caption{... \ja{What is this?}}
\end{center}
\end{figure}
